Indirect Conflicts: An Exploration and Discussion of Tools, Process, and Developer Insight

### 2013-09-30 iced-2013/paper.tex
ICED new abs, intro, methodology.

Developer awareness techniques have been proposed and studied to aid in developer
understanding and  efficient developer output in terms of source code produced. These techniques
involve the sharing of information regarding source code changes in a specific project in order
to either catch potential issues before they are fully integrated or to help developers debug
pre-existing issues. These techniques have largely focused on either \textit{direct} or 
\textit{indirect conflict} issues. While the techniques and tools for direct conflicts have had
large success, tools either proposed or studied which focus on indirect conflicts have had many common
struggles and poor developer interest. To better understand why indirect conflict tools either fail or have little
developer investment, we performed a grounded theory study with 97 developers involved in either
interviews or a web survey. We identified the main features that characterize indirect conflict issues,
what processes and techniques developers use to aid in preventing and solving indirect conflict issues,
and what developers would look for in a tool to aid them in these conflicts.

@@

As Software Configuration Management (SCM) has grown over the years, the maturity and norm of parallel 
development has become the standard development process instead of the exception. With this parallel development
comes the need for larger awareness among developers to have ``an understanding of the activities of others
which provides a context for one's own activities''~\cite{Dourish:1992:ACS}. This added awareness in theory
mitigates the downside of parallel development which is the cost of conflict prevention and resolution, however,
in practice we see these mitigated losses appear quite frequently. Not only do these conflicts still occur,
but at times they can prove to be a significant and time-consuming chore for developers~\cite{Perry:2001:PCL}.

Two types of conflicts have attracted the attention of academics over the years, \textit{direct} and 
\textit{indirect conflicts}. Direct conflicts involve immediate workspace concerns such as developers editing the same
artifact, finding expert knowledge about a particular file, or knowing when another developer is working on
the same file as you. Tools have been created and studied for these types of issues
~\cite{Xiang:2008:ERT, Biehl:2007:FVD, Sarma:2009:TIV, Khurana:2009:PFC} with relatively good success and 
positive developer feedback. However, indirect conflict tools have not had the same success. Indirect conflicts
can arise in source code for such reasons as having one's own code negatively affected by a library upgrade or
making a code change only to find out it had negative effects on unit or integration test or  having negative effects
on the way other developer's have interpreted the use of your code. Tools that have attempted to either
help developers prevent or solve indirect conflicts have either attracted little developer interest or have
had some common struggles which remain to be studied or solved.

The inherent difficulty regarding indirect conflicts is one, to determine which software dependencies are
causing indirect conflicts, and two, to be able to analyze these dependencies, specifically as to when they change
and whether or not they will induce an indirect conflict or otherwise negative consequences of a software project.
Sarma et al.~\cite{Sarma:2007:TSA} have devised a tool (Palantir) which can both detect potential indirect conflicts and alert
developers to these conflicts arising in their software projects at the class signature level. Ariadne~\cite{Trainer:2005:BGT}, another indirect 
conflict tool, creates an exploratory environment where developers can see what areas of a project they are affecting with
source code changes at the method level and thus where indirect conflicts may occur. 
Another tool developer for indirect conflicts is CASI~\cite{Servant:2010:CPI}
which utilizes dependency slicing~\cite{Bajracharya:2009:SIS} instead of the more traditional method call graphs to provide 
again an environment to see what areas of a project are being affected by a source code change. 
These tools have all shown to have the same common difficulty of scalability in the face of information overload. Too many
dependencies with the potential for indirect conflicts are being reported to developers to the point where the number of false
positives reported becomes unbearable. Our own unpublished tool Impact!~\footnote{https://github.com/jordanell/Impact} also suffered this same fate.

Many indirect conflict tools support the idea of a socio-technical congruence~\cite{Kwan:2011:ESC} in order to help
developers solve their indirect conflict issues through the means of other 
developers~\cite{Begel:2010:CDE}~\cite{Borici:2012:CHA}. Common issues arise here in that developers do not always
utilize others to solve issues, socio-technical congruence is largely unproven in regards to its correlation to
software quality~\cite{Kwan:2011:SCE} and again the problem with scalability in that many many developers may be linked to
anyone particular persons work. Again the notion of confirmation overload becomes apparent and false positives become a large
concern.

We are interested in exploring three main areas in the hopes of resolving some of the issues that are occurring
with indirect conflict tools: the nature of these conflicts in the how, what, and where, the processes that
developers use prevent, catch, and solve indirect conflicts, and what developer opinions are on preventative 
indirect conflicts tools as well as what they would look for in any tool for indirect conflicts. We broke
these categories down into the following 8 research questions:

\begin{description}
	\item[RQ1\namedlabel{itm:rq1}{RQ1}] \textit{How do indirect conflicts occur?}
	\item[RQ2\namedlabel{itm:rq2}{RQ2}] \textit{How often do indirect conflicts occur and at what times in a project do they occur more frequently?}
	\item[RQ3\namedlabel{itm:rq3}{RQ3}] \textit{What software artifacts and environments are susceptible to indirect conflicts?}
	\item[RQ4\namedlabel{itm:rq4}{RQ4}] \textit{How do developer prevent indirect conflicts?}
	\item[RQ5\namedlabel{itm:rq5}{RQ5}] \textit{How do developers catch indirect conflicts?}
	\item[RQ6\namedlabel{itm:rq6}{RQ6}] \textit{How to developers react to and solve indirect conflicts?}
	\item[RQ7\namedlabel{itm:rq7}{RQ7}] \textit{When are preemptive indirect conflict tools best used and what would developers want from them?}
	\item[RQ8\namedlabel{itm:rq8}{RQ8}] \textit{What kinds of tools do developers want to help them handle and solve indirect conflicts?}
\end{description}

We interviewed 19 developers from across 12 companies and open source projects as well as surveyed 78 
developers in order to answer these questions. Our findings indicate that while indirect conflicts are very much a real problem
in software development, developers already poses the tools to prevent and catch indirect conflicts to a certain manageable degree and have
the mindset of working until something breaks, then attempting a fix. Thus, developers would rather spend their time developing instead
of taking or reading preventative measures, resulting in the need of tools to debug and solve indirect conflicts quickly
(reactionary tools) as opposed to tools which attempt to prevent or catch indirect conflicts early (preemptive tools).

We continue this paper by first presenting our summarized methodology we used to perform this study in Section~\ref{sec:meth}. We
continue with the results of our study in regards to our 8 research questions in Section~\ref{sec:results} 
followed by a discussion in Section~\ref{sec:disc} of what was found and how it can be applied to future study and implementation
of indirect tools or processes. We next present how evaluation was performed in terms of the credibility
and quality of our results in Section~\ref{sec:eval}, then cover related work in Section~\ref{sec:related}
and conclude in Section~\ref{sec:conc}.

@@

Our grounded theory study was performed in two parts. First, a round of semi-structured interviews were conducted which 
addressed the larger who, what, when, where, and how about indirect conflicts. Secondly, a survey was given
out which was used to confirm what was theorized from the interviews on a larger sample size as well as obtain
larger developer opinion.

\subsection{Grounded Theory}
We approached our study based on grounded theory as described by Corbin and Strauss~\cite{Corbin:1998:SP}.
Grounded theory is a qualitative research methodology that utilizes \textit{theoretical sampling} and
\textit{open code} to create a social theory ``grounded'' in the empirical data. For an exploratory study such as
the ours, grounded theory is well suited because involves starting from very broad and abstract type questions and
making refinements along the way as the study progresses and hypotheses begin to take shape. Grounded theory involves
regining the sampling criteria throughout the course of the study to ensure that participants are able to answer new
questions that have been formulated in regards to forming hypotheses. In our study being presented, data collected from
both interviews and surveys (when open ended questions were involved) was analyzed using open coding. Open coding involves
assigning codes to what participants said at a low sentence level or abstractly at a paragraph or full answer level. These
codes were defined as the study progressed and different hypotheses began to grow. We finally use axial coding it order to
link our defined codes to categories of grounded theory such as context and consequences. The ultimate goal of grounded 
theory is to produce a theory that is tied to the empirical data collected; our final theories can be seen in
findings~\ref{itm:f1} -~\ref{itm:f9}. In Section~\ref{sec:eval}, we give a brief evaluation of our studying using 
3 criteria that are commonly used in evaluating grounded theory studies.

@@

We selected our interview participants from a large breadth of both open and closed source software development companies
and projects. The population which participated in our interview came from the following software groups: 
IBM, Mozilla, The GNOME Project, Microsoft Corporation, Subnet Solutions, Ruboss Technology Corporation, 
Amazon, Exporq Oy, Kano Apps, Fireworks Design, James Evans and Associates, and Frost Tree Games. 
Our participants we chosen based on their direct involvement in the actual writing of software for
their respective companies or projects. These participants' software development titles included: senior developer,
lead developer, software developer, software developer in test, and junior developer.
In addition to software development, some participants were also chosen based on their previous experience
of software development as well as their current experience with project management at some capacity. These management
type participants involved in project planning to some capacity between technical architecture, project maintainer,  
chief technical officer, or program manager.

@@

Participants were invited to participate in the interviews by email and were sent a single reminder email one week
after the initial invitation if no response had been made. We directly emailed 22 participants and ended up conducting
19 interviews. Interviews were conducted in person when possible and recorded for audio content only. When in person
interviews were not possible, one of Skype or Google Hangout was used with audio and video being recorded but only
audio being stored for future use. We were quite pleased with the response rate to our initial invitation emails as
our breadth of participants was rather large spanning multiple open and closed source project and our interview 
answer saturation~\cite{Guest:2006:SAP} was quite high (to be seen in Section~\ref{sec:results}).

Interview participants first answered a number of structured demographic items. Next, participants were 
asked to describe various software development experiences regarding our three main areas of focus: the nature
of indirect conflicts, current processes used regarding indirect conflicts, opinions on future and the use of
current tools. processes they use or encounter in their current working environment. These three areas of focus
were studied by having the interview participants talk about their experiences and opinions in the following
\totalCategories{} semi-structured research topics which were asked of:

\begin{itemize}
\item Software development tools for dependency tracking and awareness.
\item Software development process for preventing indirect conflicts.
\item Software artifact dependency levels and where conflicts can arise.
\item How developers find internal or external software dependencies.
\item Examples of indirect conflicts from real world experiences.
\item How indirect conflicts are detected and found.
\item How indirect conflict issues are solved or dealt with.
\item Developer opinion of preemptive measures to prevent indirect conflicts.
\item Developer opinion on what types of changes are worth a preemptive action.
\item Developer opinion on who is responsible for fixing or preventing indirect conflicts.
\end{itemize}

While each of the \totalCategories{} question categories had a number of starter questions, interviews 
largely became discussions of developer experience and opinion as opposed to direct answers to any specific question.
In general, once the category was explained to the participant, little prompting was necessary as the participant
would jump right into an experience, or issue he or she had with the question or category. However, not all
participants had strong opinions or any experience on every category mentioned. For these participants, answers 
to the specific categories were not required or pressed upon. We attribute any non answer by a participant to
either lack of knowledge in their current project pertaining to the category or lack of experience in terms of
being apart of any one software project for extended periods of time. We account for these non answers
in our analysis and results as seen in Section~\ref{sec:results}. Interviews lasted 
from 15 minutes up to 75 minutes. The length of the interview largely depended on the amount of experience the
participant had in software development as they were able to give more experiences and more informed opinions.

@@

We selected our survey participants from a similar breadth of open and closed source software development 
companies and projects as the interviews participants with two large exceptions. The software organizations
that remained the same between interview and survey were: Mozilla, The GNOME Project, Microsoft Corporation, 
Subnet Solutions, and Amazon.
However, participants who took part in the round of interviews were not asked to participate in the surveys but
rather to act as a contact point for other developers in their team, project, or organization who may be interested
in completing the survey. Aside from this aforementioned list, two large groups of developers were asked to
participate as well, these being GitHub users as well as Apache Software Foundation (Apache) developers. The GitHub
users were selected based on large amounts of development activity on GitHub and the Apache developers
were selected based on their software development participation on specific projects known to be used heavily
utilized by other organizations and projects.

@@

The created survey was based off of the \totalCategories{} categorical hypotheses given by the round of interviews. The survey
was designed to test these hypotheses and to acquire a larger sample size of developers who may have similar
or different opinions from those already acquired from the interviews. The survey went through two rounds of
piloting. Each pilot round consisted of five participants, who were previously interviewed, completing the survey
with feedback given at the end. The previous interview participants were selected based on their domain knowledge
expertise with indirect conflicts in order to provide what we think would be amount to better feedback and resulting
in a more polished survey. This also allowed the previously interviewed developers to examine what hypotheses were
formed and we would be moving forward with. The final survey consisted of the following:
2 multiple choice questions for developer experience and demographic information; 3 level of agreement questions for an indication of
what types of environments indirect conflicts are more likely to occur;
6 level of use questions to indicate what types of software changed developers find trouble some with respect to
indirect conflicts; and 9 short answer questions for indication of when indirect conflicts occur, what types of
processes are used to prevent or react to indirect conflict, and to provide an outlet for general opinion
on the matter. Each non demographic question was made optional as it was shown 
through the interviews that some questions require more experience from participants than may be provided.

Survey participants were invited to participate in the survey by email. No reminder email was ever sent as the
survey responses were not connected with the invitation email addresses and thus participants who did respond
could not be removed from a reminder list. We directly emailed 1300 participants and ended with 78 responses
giving a response rate of 6\%. We attribute the low response rate with a couple of factors. One, the surveys
were conducted during the months of July and August while many participants may be away from their regular positions.
Two, our GitHub and Apache participants could not be verified as to whether or not they actively support the
email addresses used in the invitations. And finally, the survey was considered by some to be long and require
more development experience than may have been typical of some of those invited to participate.

@@

Following our data collection and analysis, we re-interviewed some of our initial interview participants
in order to validate our findings. We confirmed our hypotheses as to whether or not they resonate with 
industry participants' opinions and experiences regarding indirect conflicts and as to their industrial 
applicability. Due to limited time constraints of the interviewed participants, we could only re-interview
five participants. Those that were re-interviewed came from the range of 5-10 years of software development
experience. Re-interviewed participants were given our 8 research questions along with results and 9 findings
and asked open ended questions regarding their opinions and experiences to validate our findings. The five
participants found FILL IN HERE WHEN COMPLETE.

>>>>

Awareness techniques have been proposed and studied to aid in developer
understanding, efficiency, and quality of software produced. Some of these techniques have focused 
on either \textit{direct} or 
\textit{indirect conflicts} in regards to prevent, catching, or debugging these conflicts as they arise
through source code changes. While the techniques and tools for direct conflicts have had
large success, tools either proposed or studied for indirect conflicts have had many common
struggles and little developer interest. To better understand common indirect conflict tool issues, 
we performed a grounded theory study with 97 developers involved in either
interviews or a web survey. We found that: indirect conflicts are a real and frequent problem,
developers already posses a large suite of tools and processes which can prevent and catch
indirect conflicts at a manageable scale, and that developers have a work until something breaks philosophy
which leads to the lesser want of prevention tool as to the want of quick and perhaps automatic debugging tools
for indirect conflicts.

@@

As Software Configuration Management (SCM) has grown over the years, the maturity and norm of parallel 
development has become the standard development process instead of the exception. With this parallel development
comes the need for larger awareness among developers to have ``an understanding of the activities of others
which provides a context for one's own activities''~\cite{Dourish:1992:ACS}. This added awareness
mitigates some downsides of parallel development which include the cost of conflict prevention and resolution, however,
in practice we see these mitigated losses continue to appear quite frequently. Not only do these conflicts still occur,
but at times they can prove to be a significant and time-consuming chore for developers~\cite{Perry:2001:PCL}.

Two types of conflicts have attracted the attention of academics over the years, \textit{direct} and 
\textit{indirect conflicts}. Direct conflicts involve immediate workspace concerns such as developers editing the same
artifact, or finding expert knowledge about a particular file. Tools have been created and studied for direct conflicts
~\cite{Xiang:2008:ERT, Biehl:2007:FVD, Sarma:2009:TIV, Khurana:2009:PFC} with relatively good success and 
positive developer feedback. However, indirect conflict tools have not shared the same success. Indirect conflicts
can arise in source code for such reasons as having one's own code negatively affected by a library upgrade,
making a code change only to find out it had negative effects on unit or integration test, or having negative effects
on the way other developer's have interpreted the use of your code. Tools that have attempted to either
help developers prevent or solve indirect conflicts have either attracted little developer interest or have
had some common struggles which remain to be studied or solved.

Difficulties regarding indirect conflicts are to determine when software dependencies change and more crucially,
when those changes will create negative consequences in a software project.
Sarma et al.~\cite{Sarma:2007:TSA} built Palantir, which can both detect potential indirect conflicts, at the class signature level,
and alert developers to these conflicts. Holmes et al.~\cite{Holmes:2010:CAR} take it
one step further with their tool YooHoo by detecting fine grained source code changes, such as method return type changes, 
and create a taxonomy for different
types of changes and their proneness to cause indirect conflicts. The tool Ariadne~\cite{Trainer:2005:BGT} 
creates an environment where developers can see how source code changes will affect other areas of a project at the 
method level and thus where indirect conflicts may occur. 
Another indirect conflict tool, CASI~\cite{Servant:2010:CPI},
utilizes dependency slicing~\cite{Bajracharya:2009:SIS} instead of method call graphs to provide 
an environment to see what areas of a project are being affected by a source code change. 
Most of these tools have all shown to have common difficulties of: scalability, false positives, information overload, 
or providing redundant information to preexisting tools. 
Our own tool Impact!~\footnote{https://github.com/jordanell/Impact} also suffered these same fates.

Since Cataldo et al.~\cite{Cataldo:2006:ICR} have shown that socio-technical congruence can be leveraged to improve task completion
times, many indirect conflict tools support the idea of a socio-technical congruence~\cite{Kwan:2011:ESC} in order to help
developers solve their indirect conflict issues through social means~\cite{Begel:2010:CDE}~\cite{Borici:2012:CHA}. 
However, socio-technical congruence is largely unproven in regards to its correlation to
software quality~\cite{Kwan:2011:SCE} and again the problems of scalability and information overload become a factor.

We are interested in exploring three questions in the hopes of resolving some of the issues that are occurring
with indirect conflict tools:

\begin{description}
	\item[RQ1\namedlabel{itm:rq1}{RQ1}] \textit{What is the nature of indirect conflicts?}
	\item[RQ2\namedlabel{itm:rq2}{RQ2}] \textit{What types of process and tools are being used by developers in regards to indirect conflicts?}
	\item[RQ3\namedlabel{itm:rq3}{RQ3}] \textit{How should indirect conflict tools work to best benefit developers?}
\end{description}

We interviewed 19 developers from across 12 companies and open source projects as well as surveyed 78 
developers in order to answer the aforementioned questions. Our findings indicate that while indirect conflicts are very much a real 
and frequent problem
in software development, developers already posses the tools to prevent and catch indirect conflicts to a manageable degree and have
the mindset of working until something breaks, then attempting a fix. Thus, developers would rather spend their time developing instead
of taking or reading preventative measures, resulting in the need of tools to debug and solve indirect conflicts quickly as opposed to tools 
which attempt to prevent or catch indirect conflicts early.

We continue this paper by first presenting our summarized methodology we used to perform this study in Section~\ref{sec:meth}. We
then explain and discuss the results of our study in regards to our 3 research questions in Section~\ref{sec:results}.
Next, an evaluation of how our study was performed in terms of the credibility
and quality of our results is described in Section~\ref{sec:eval}. We then cover related work in Section~\ref{sec:related}
and conclude in Section~\ref{sec:conc}.

@@

Our grounded theory study was performed in two parts. First, a round of semi-structured interviews were conducted which 
addressed the 3 research questions as mentioned above. Secondly, a survey was conducted
which was used to confirm and test what was theorized from the interviews on a larger sample size as well as obtain
larger developer opinion of the subject.

\subsection{Grounded Theory}
We approached our study based on grounded theory as described by Corbin and Strauss~\cite{Corbin:1998:SP}.
Grounded theory is a qualitative research methodology that utilizes \textit{theoretical sampling} and
\textit{open coding} to create a theory ``grounded'' in the empirical data. For an exploratory study such as
the ours, grounded theory is well suited because it involves starting from very broad and abstract type questions and
making refinements along the way as the study progresses and hypotheses begin to take shape. Grounded theory involves
realigning the sampling criteria throughout the course of the study to ensure that participants are able to answer new
questions that have been formulated in regards to forming hypotheses. In our study being presented, data collected from
both interviews and surveys (when open ended questions were involved) was analyzed using open coding. Open coding involves
assigning codes to what participants said at a low sentence level or abstractly at a paragraph or full answer level. These
codes were defined as the study progressed and different hypotheses began to grow. We finally use axial coding it order to
link our defined codes through categories of grounded theory such as context and consequences. The ultimate goal of grounded 
theory is to produce a theory that is tied to the empirical data collected; our final theories can be seen in
findings~\ref{itm:f1} -~\ref{itm:f9}. In Section~\ref{sec:eval}, we give a brief evaluation of our studying using 
3 criteria that are commonly used in evaluating grounded theory studies.

@@

We selected our interview participants from a large breadth of both open and closed source software development companies
and projects. The population which participated in our interview came from the following software groups: 
IBM, Mozilla, The GNOME Project, Microsoft Corporation, Subnet Solutions, Ruboss Technology Corporation, 
Amazon, Exporq Oy, Kano Apps, Fireworks Design, James Evans and Associates, and Frost Tree Games. 
Our participants we chosen based on their direct involvement in the actual writing of software for
their respective companies or projects. These participants' software development experience ranged from 3-25 years of experience
with an average of 8 years of experience.
In addition to software development, some participants were also chosen based on both their experience of software development 
as well as their experience with project management at some capacity.

@@

Participants were invited to participate in the interviews by email and were sent a single reminder email one week
after the initial invitation if no response had been made. We directly emailed 22 participants and ended up conducting
19 interviews. Interviews were conducted in person when possible and recorded for audio content only. When in person
interviews were not possible, one of Skype or Google Hangout was used with audio and video being recorded but only
audio being stored for future use. We were pleased with the response rate to our initial invitation emails as
our breadth of participants was rather large, spanning multiple open and closed source, Agile and Waterfall based projects,
and our interview answer saturation~\cite{Guest:2006:SAP} was quite high.

Interview participants first answered a number of structured demographic items. Next, participants were 
asked to describe various software development experiences regarding our three research questions.
Our three questions were studied by having the interview participants talk about their experiences and opinions in the following
\totalCategories{} semi-structured research topics:

\begin{itemize}
\item Examples of indirect conflicts from real world experiences.
\item Software artifact dependency levels and where conflicts can arise.
\item Software development tools for dependency tracking and awareness.
\item Software development process for preventing indirect conflicts.
\item How developers find internal or external software dependencies.
\item How indirect conflicts are detected and found.
\item How indirect conflict issues are solved or dealt with.
\item Developer opinion of preemptive measures to prevent indirect conflicts.
\item Developer opinion on what types of changes are worth a preemptive action.
\item Developer opinion on who is responsible for fixing or preventing indirect conflicts.
\end{itemize}

While each of the \totalCategories{} question categories had a number of starter questions, interviews 
largely became discussions of developer experience and opinion as opposed to direct answers to any specific question.
However, not all participants had strong opinions or any experience on every category mentioned. For these participants, answers 
to the specific categories were not required or pressed upon. We attribute any non answer by a participant to
either lack of knowledge in their current project pertaining to the category or lack of experience in terms of
being apart of any one software project for extended periods of time. We account for these non answers
in our analysis and results as seen in Section~\ref{sec:results}. Interviews lasted 
from 15 minutes up to 75 minutes and were very much dependent on the experience of the participant.

@@

We selected our survey participants from a similar breadth of open and closed source software development 
companies and projects as the interviews participants with two large exceptions. The software organizations
that remained the same between interview and survey were: Mozilla, The GNOME Project, Microsoft Corporation, 
Subnet Solutions, and Amazon.
However, participants who took part in the round of interviews were asked to act as a contact point for other 
developers in their team, project, or organization who may be interested
in completing the survey. Aside from this aforementioned list, two groups of developers were asked to
participate as well, these being GitHub users as well as Apache Software Foundation (Apache) developers. The GitHub
users were selected based on large amounts of development activity on GitHub and the Apache developers
were selected based on their software development contributions on specific projects known to be used heavily
utilized by other organizations and projects.

@@

Survey participants were invited to participate in the survey by email. No reminder email was sent as the
survey responses were not connected with the invitation email addresses and thus participants who did respond
could not be identified. We directly emailed 1300 participants and ended with 78 responses
giving a response rate of 6\%. We attribute the low response rate with: the surveys
were conducted during the months of July and August while many participants may be away from their regular positions.
and our GitHub and Apache participants could not be verified as to whether or not they actively support the
email addresses used in the invitations. In addition, the survey was considered by some to be long and require
more development experience than may have been typical of some of those invited to participate.

The created the survey was based off of categorical hypotheses created by the round of interviews. The survey
was designed to test these hypotheses and to acquire a larger sample size of developers who may have similar
or different opinions from those already acquired from the interviews. The survey went through two rounds of
piloting. Each pilot round consisted of five participants, who were previously interviewed, completing the survey
with feedback given at the end. Not only did this allow us to create a more polished survey, but it also allowed the previously interviewed developers to examine what hypotheses were
formed and what we would be moving forward with. The final survey consisted of:
2 multiple choice questions for demographic information; 3 level of agreement questions for an indication of
what types of environments indirect conflicts are more likely to occur;
6 level of use questions to indicate what types of software changed developers find trouble some with respect to
indirect conflicts; and 9 short answer questions for indication of when indirect conflicts occur, what types of
processes are used to prevent or react to indirect conflict, and to provide an outlet for general opinion
on the matter. Each non demographic question was made optional as it was shown 
through the interviews that some questions require more experience from participants than may be provided.

@@

Following our data collection and analysis, we re-interviewed some of our initial interview participants
in order to validate our findings. We confirmed our hypotheses as to whether or not they resonate with 
industry participants' opinions and experiences regarding indirect conflicts and as to their industrial 
applicability. Due to limited time constraints of the interviewed participants, we could only re-interview
five participants. Those that were re-interviewed came from the range of 5-10 years of software development
experience. Re-interviewed participants were given our 3 research questions along with results and 9 findings,
and asked open ended questions regarding their opinions and experiences to validate our findings. The five
participants found FILL IN HERE WHEN COMPLETE.
